AbxD01 Analysis

### 2014-11-13 abxD01_analysis.Rmd
backup

---
title: "AbxD01 Analysis"
author: "Alyx Schubert"
date: "September 29, 2014"
output: word_document
---

@@

>>>>

---
title: "AbxD01 Analysis"
author: "Alyx Schubert"
date: "September 29, 2014"
output: pdf_document
---

@@

## Figure 6

This figure shows the results of our model predicting *C. difficile* colonization given relative abundances of a subset of bacteria.

### TO DO STILL
- Make figure!
